Time for a rethink: disparity-through-time

### 2017-12-01 manuscript/time-slice.tex
title suggestion + affiliation

\title{Time for a rethink: disparity-through-time}

\author{
	Thomas Guillerme$^{1*}$ and Natalie Cooper$^{2}$
}

@@

\affiliation{\noindent{\footnotesize
	$^1$Thomas address\\ 
	$^2$Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK. natalie.cooper@nhm.ac.uk}\\
	$^*$Corresponding author\\}

>>>>

\title{Time for a rethink: disparity-through-time}
%TG: Great title first part! How about changing the other part to 
%Time for a rethink: different ways of slicing through the stratigraphic cake leads to different disparity through time results.

\author{
	Thomas Guillerme$^{1*}$ and Natalie Cooper$^{2}$
}
%TG: authorship-wise it's up to you, in the end, since it's just the two of us, I think it really doesn't matter (i.e. it's still gonna be Cooper Guillerme or Guillerme Cooper), I'll hopefully will have a couple of first author papers coming up for 2018 so up to you if you want one as well.

@@

\affiliation{\noindent{\footnotesize
	$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
	$^2$Department of Life Sciences, Natural History Museum, Cromwell Road, London, SW7 5BD, UK. natalie.cooper@nhm.ac.uk}\\
	$^*$Corresponding author\\}
